\documentclass[letterpaper, 11pt]{article}
\makeatletter
\providecommand*{\input@path}{}
\g@addto@macro\input@path{{../}}
\makeatother
\usepackage[left=2cm, right=2cm, top=2cm, bottom=2cm]{geometry}
\usepackage{titling}
\setlength{\droptitle}{-5em}

% Packages not loaded by std_page.tex but required for article document class
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{longtable}
\usepackage{booktabs}
\usepackage{array}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}

% Input workspace custom packages and commands
\input{../ltx_core/ltx_pkgs.tex}
\newcommand{\bm}{}
\input{../ltx_core/new_cmds.tex}

\newenvironment{reviewercomment}
{\begin{framed}\noindent\textbf{Reviewer Comment:}\itshape}
{\end{framed}}

\title{Author Responses to Peer Reviews \\ \large Joint MECC 2026 -- ASME JDSMC Submission \#26}
\author{Sesha Charla, Peter H. Meckl, Bin Yao}
\date{\today}

\begin{document}
\maketitle

We thank the Associate Editor and the reviewers for their constructive feedback and valuable suggestions on our
manuscript. We have carefully revised the manuscript to address all the points raised. Below we provide responses to
each of the specific comments and describe the corresponding revisions made in the paper.

\renewcommand{\arraystretch}{1.3}
\begin{longtable}{>{\raggedright\arraybackslash}p{0.15\textwidth}>{\raggedright\arraybackslash}p{0.35\textwidth}>{\raggedright\arraybackslash}p{0.45\textwidth}}
    \toprule
    \textbf{Reviewers}                                                                                                                       &
    \textbf{Reviewer Feedback}                                                                                                               &
    \textbf{Rebuttal Comments and Actions}                                                                                                     \\ \midrule
    \endfirsthead
    \toprule
    \textbf{Reviewers}                                                                                                                       &
    \textbf{Reviewer Feedback}                                                                                                               &
    \textbf{Rebuttal Comments and Actions}                                                                                                     \\ \midrule
    \endhead
    \bottomrule
    \endfoot
    Associate editor,\newline Reviewer 12,\newline Reviewer 14                                                                               &
    Formatting errors and Writing issues.                                                                                                    &
    1. The writing issues are due to missed reference link while changing the paper format from JDSMC template to MECC template. These are fixed. \newline
    2. The chemical symbols are corrected from being italic in math mode to roman format as suggested by Reviewer 14.                          \\ \midrule
    Reviewer 18                                                                                                                              &
    Independence of saturated mode's dynamics on previous states.                                                                            &
    The goal of the phrase was to convey that one mode (saturated) of the switched dynamic model for NOx reduction is independent of initial conditions so, we can use the prediction error to classify data points as ``close to saturation" for working out the statistics for aging detection. \newline\newline
    Clarified this by adding more information to the referred sentences (first paragraph of section 4).                                        \\ \midrule
    Reviewer 14                                                                                                                              &
    Interpretation of threshold $\beta$: Why is the threshold abruptly scaled to 250 for truck data?                                         &
    The limited sample size causes $T_w$ to diverge from its asymptotic $\chi^2_\nu$ distribution under $\mathcal{H}_0$.
    \newline\newline
    Added 2 paragraphs at the end of section-6 justifying the reason for threshold discrepancy.                                                \\
    \midrule
    Associate Editor,\newline Reviewer 18,\newline Reviewer 14                                                                               &
    \textbullet~ Explain the bottleneck of utilizing the limited data for diagnostics in the context of real-world applications? \newline
    \textbullet~ What operating conditions would ensure this necessary conditions are satisfied? \newline
    \textbullet~ How long is the system expected to wait for OBD decision? \newline
    \textbullet~ Under driving conditions that do not trigger catalyst saturation, will the system generate false alarms?                    &
    Although only a fraction of the operating data is close to saturation (approximately 10\% in real-world truck data),
    the convex parameter estimation framework utilizes the \textbf{entire} dataset. The non-saturated data points
    establish the lower boundary constraints ($\eta(k) \le \eta_{\sat}(k)$), which restrict the parameter space and
    prevent the estimates from collapsing.
    \newline\newline
    Explicitly addressed the comments about dealing with the engineering limitations of the necessary conditions at the end of section 6       \\ \midrule
    Reviewer 12                                                                                                                              &
    Significance of the paper should be stated clearly                                                                                       &
    Separated the contributions to a separate paragraph at the end of Introduction.                                                            \\ \midrule
    Reviewer 12                                                                                                                              &
    The reader may want a clear comparison between experimental results and the model results. It is better to present figures than numbers. &
    Tables are utilized instead of time-series figures to convey the massive amount of detection results clearly and concisely.                \\ \midrule
    Reviewer 12                                                                                                                              &
    Literature review is not sufficient. Limitations of the existing works are not clear.                                                    &
    As this paper focuses specifically on the narrow aspect of model-based SCR aging diagnostics under catalyst saturation. The current literature review and the included references justify the research objctive, idetify the gap and map directly to this specific focus. We believe the existing references adequately represent the state-of-the-art for this particular diagnostic approach.
    \\ \bottomrule
\end{longtable}

\end{document}
