\section{Aging Detection from Truck Data}
%===
The performance of the proposed aging detector is also demonstrated using the $\nox$ sensor data from four long-haul
trucks. The road data were collected from trucks operating in the United States for two days separated by a few years
(Table~\ref{tab::truck_data_summary}) during which the catalyst had aged based on existing performance measures. The
data has measurements of $\nox$ sensors before and after the catalyst, as well as other required variables
including flow rate, temperature and urea injection rate. The data preprocessing includes,
\begin{inparaenum}
        \item removing the rows with missing values,
        \item removing the rows whose operating temperature range is beyond the range of $200-300 \,^\circ C$,
        \item interpolating the missing data if the data gaps are smaller than a minute, and finally,
        \item smoothing the data using a non-causal Chebyshev filter.
\end{inparaenum}
The preprocessed data is then partitioned into drive segments with no breaks, which correspond to a continuous driving
period from engine start to engine stop.
%===
% Truck Mapping
% Truck A - AD Transport (adt)
% Truck B - Mesilla Valley (mes)
% Truck C - Werner (wer)
% Truck D - Transwest (trw)
% =====
\begin{table}[ht]
        \centering
        \caption{Truck Data Set Years and Mileage Difference}
        \label{tab::truck_data_summary}
        \begin{tabular}{c c c c}
                \hline \hline
                Truck   & Earlier Data & Latter Data & Mileage            \\
                        & Year         & Year        & Difference         \\ \hline \hline
                Truck A & $2015$       & $2017$      & $2.8 \times 10^5$  \\
                Truck B & $2015$       & $2018$      & $11.9 \times 10^5$ \\
                Truck C & $2015$       & $2017$      & $5.9 \times 10^5$  \\
                Truck D & $2015$       & $2016$      & $6.6 \times 10^5$  \\
                \hline \hline
        \end{tabular}
\end{table}
%===
Unlike the test-cell data where the engine drive-cycles are repeatable and produce a significant fraction of samples where the catalyst is close to saturation, the truck data drive segments constitute varied driving conditions with fewer samples $\lrf{\leq 10\%}$ that are close to catalyst saturation. A necessary condition for the proposed parameter estimation and aging detection framework is that the data has a sufficiently large number of samples close to catalyst saturation such that the asymptotic properties of the MLE and the test statistic hold (\ref{eqn::Ns_min}). Hence, the drive segment data are further pruned to only include segments with at least $150$ samples ($120$ in the case of Truck C) close to catalyst saturation.
\begin{align}
        N_{sat}       & \geq N_{sat}^{min} \label{eqn::Ns_min} \\
        \beta_{truck} & = 250 \label{eqn::beta_truck}
\end{align}
The threshold of the Wald test statistic (\ref{eqn::beta_truck}) for aging detection in trucks is chosen such that it
maximizes the probability of detection while minimizing the probability of false alarm and missed detection for the
given limited truck data. The value of the test statistic for the drive segments for each truck is tabulated in
Tables~\ref{tab::adt_aging_res}, \ref{tab::mes_aging_res}, \ref{tab::wer_aging_res} and \ref{tab::trw_aging_res}. A
summary of the aging detection results is tabulated in Table~\ref{tab::truck_aging_summary}. The detector performs
reasonably well on three of the four trucks with high probability of detection and low false alarm and missed detection
rates. Truck A has relatively lower mileage difference between the earlier and latter data years which may explain the
lower detection performance. The performance is limited by the amount of data available with sufficient samples close to
catalyst saturation. Further, the lack of ground truth on the actual individual catalyst's aging levels limits the
ability to quantify the performance of the detector.
%===
\begin{table}[ht]
        \centering
        \caption{Summary of Aging Detection Results on Truck Data}
        \label{tab::truck_aging_summary}
        \begin{tabular}{c c c c c}
                \hline \hline
                Truck   & Total Drive & Detection & False & Missed    \\
                        & Segments    &           & Alarm & Detection \\\hline \hline
                Truck A & 8           & 4         & 0     & 4         \\
                Truck B & 11          & 9         & 1     & 1         \\
                Truck C & 9           & 7         & 1     & 1         \\
                Truck D & 8           & 6         & 2     & 0         \\
                \hline \hline
        \end{tabular}
\end{table}
%===

The threshold $\beta_{truck} = 250$ is significantly larger than the test-cell thresholds ($\beta_{RMC} = 10$,
$\beta_{hFTP} = 4$) because the limited sample size causes $T_w$ to diverge from its asymptotic $\chi^2_\nu$
distribution under $\mathcal{H}_0$. The convergence of the MLE to normality depends on the number of saturated-mode
samples \cite{kay1993estimation}, and truck data has considerably fewer such samples ($N_{sat} \approx 120$-$150$)
compared to test-cell experiments ($N_{sat} \approx 200$-$500$), resulting in heavier tails in the null distribution of
$T_w$. This effect is compounded by the less reliable estimation of the error variance under road conditions and the
unaccounted variance of the reference parameter $\theta_{sat}^{dg}$, which is itself estimated from limited data. Both
factors inflate $T_w$ under $\mathcal{H}_0$, necessitating a higher threshold to maintain an acceptable false-alarm
rate.

With a larger data set and known degreened paramters, the thresholds can be determined using statistically-optimal
selection criteria such as Neyman-Pearson \cite{kay1998detection} or minimum Bayes cost on the receiver operating
characteristic (ROC) curve \cite{PoorDetection}. This would require multiple truck runs under known catalyst conditions
to characterize the null distribution, and runs at known aging levels to estimate the non-centrality parameter under
$\mathcal{H}_1$. Nevertheless, the results demonstrate that the proposed saturated-catalyst model (\ref{eqn::nox_mdl})
coupled with the constrained parameter estimation method (\ref{eqn::lin_prog}) and the statistical detector
(\ref{eqn::wald_test}) enables a statistically-grounded aging detection framework that performs reasonably well on both
test-cell and truck data under sensor sampling limitations and cross-sensitivity.

%=== Practical OBD considerations ===
For on-vehicle implementation, the detector's performance depends on whether the driving profile produces sufficient
data close to catalyst saturation within a given driving window. Conditions that combine moderate-to-high exhaust mass
flow rates with elevated urea dosing, such as sustained highway cruising, high-load acceleration, or uphill driving
within the detector's operational temperature range ($200$--$300\,^\circ C$ in the present case, which can be adjusted),
are most likely to trigger saturation. The extent of catalyst utilization can be assessed in real time by monitoring
readily-available signals such as urea dosing rate, engine rpm, and the estimate of $\nox$ reduction from sensors. When
these indicate sustained low $\text{NO}_x$ reduction and low urea dosing which leaves the catalyst unsaturated, the
system can determine apriori that the accumulated data are unsuitable for aging detection and defer its decision rather
than executing the hypothesis test on insufficient data. The detector therefore avoids producing false alarms under
non-catalyst-saturating driving conditions, as the Wald test~(\ref{eqn::wald_test}) is simply not invoked. A consequence
of this design is that the monitor's in-use performance ratio (IUPMR) is governed by the frequency of saturating driving
conditions, since the diagnostic can only complete when the necessary condition~(\ref{eqn::Ns_min}) is met.


